### 2019-08-28 manuscript/manuscript.tex
updates to figures, new plot code

\begin{figure}[!ht]
  \centering
  \includegraphics[width=\textwidth]{figures/figure-1.pdf}
  \caption{$B=5000$ bootstraps, with 100}
  \label{fig:figure-1}
\end{figure}

\begin{figure}[!ht]
  \centering
  \includegraphics[width=\textwidth]{figures/figure-2.pdf}
  \caption{}
  \label{}
\end{figure}

\begin{figure}[!ht]
  \centering
  \includegraphics[width=\textwidth]{}
  \caption{}
  \label{}
\end{figure}

\begin{figure}[!ht]
  \centering
  \includegraphics[width=\textwidth]{}
  \caption{}
  \label{}
\end{figure}

>>>>

\begin{figure}[!ht]
  \centering
  \includegraphics[width=\textwidth]{figures/figure-1.pdf}

  \caption{A: Temporal covariance, averaged across all ten replicate
    populations, through time from the \textcite{Barghi2019-qy} study. Each
    line depicts the temporal covariance $\cov(\Delta p_s, \Delta p_t)$ from
    some reference generation $s$ to a later time $t$ which varies along the
    x-axis; each line corresponds to a row of the upper-triangle of the
    temporal covariance matrix with the same color (upper right). The ranges
    around each point are $95\%$ block-bootstrap confidence intervals. B: The
    proportion of the total variance in allele frequency change explained by
    linked selection, $G(t)$, as it varies through time $t$ along the x-axis.
    The black line is the $G(t)$ averaged across replicates, with the $95\%$
    block-bootstrap confidence interval. The other lines are the $G(t)$ for
    each individual replicate, with colors indicating what subset of the
    temporal-covariance matrix to the right is being included in the
  calculation of $G(t)$.}

  \label{fig:figure-1}
\end{figure}

\begin{figure}[!ht]
  \centering
  \includegraphics[width=\textwidth]{figures/figure-2.pdf}

  \caption{A: The convergence correlation, averaged across replicate pairs,
    through time. Each line represents the convergence correlation
    $\mathrm{cor}(\Delta p_{s}, \Delta p_{s})$ from a starting reference
    generation $s$ to a later time $t$, which varies along the x-axis; each
  line corresponds to a row of the temporal convergence correlation matrix
depicted to the right.}

  \label{fig:figure-2}
\end{figure}

\begin{figure}[!ht]
  \centering
  \includegraphics[]{figures/figure-3.pdf}
  \caption{}
  \label{fig:figure-3}
\end{figure}

% \begin{figure}[!ht]
%   \centering
%   \includegraphics[width=\textwidth]{}
%   \caption{}
%   \label{}
% \end{figure}
